Merging Datasets Through Deep learning

### 2018-09-02 paper2018/introduction2.tex
removing some equations

As in face recognition, our system for metric learning is built by training a so-called triplet based `siamese triplet' network to learn to produce a small distance estimate for two surface forms for the same entity (between an arbitrarily chosen anchor and positive), and a large distance estimate for surface forms of different entities (an anchor and a negative).  A key problem in effective training of such networks is the problem of how to select negative pairs for training, because one cannot exhaustively show all negative pairs to the network.  In prior work for instance, this problem is solved by so-called `triplet mining' where so-called `semi-hard' negatives are gleaned after an all-pairs comparison of input vectors in a batch, e.g., \cite{DBLP:conf/cvpr/SchroffKP15}.  `Semi-hard' negatives are negatives that are further away from the anchor than positives, but not by a sufficient margin.  The idea of focusing on semi-hard negatives is to avoid mining poorly structured regions of the embedding space.  For matching across entity names, most positive forms for the entity names are actually substantially further away from the anchor than are negatives, as we show empirically in this paper.  Our approach to this problem is to use an approximate nearest neighbors algorithm to choose negatives for training in an efficient way, which means that most of the time, our negatives are `hard negatives', where the negative is closer to the anchor than positives.  This approach has three key benefits.  First, it lays out the entities based on their input vectors, and thus allows an efficient gathering of all nearest neighbors without a quadratic comparison of vectors in a batch to determine suitable negatives.  Second, it provides a baseline against which one can objectively measure the effects of training.  If for instance, the input vectors for surface forms of the same entity are already close together in vector space, little can be gained by a deep learning model.  Third, it examines whether focusing on hard negatives is really detrimental to deep metric learning, at least for learning to map entity names in vector space.

We also investigated the effect of manipulating multiple local loss functions which have been proposed in the literature for improving deep metric learning, e.g., the triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, improved loss \cite{Zhang:2016:DML:3088616.3088665}, and angular loss \cite{DBLP:journals/corr/abs-1708-01682} functions.  For the problem of building models for people's names, we found that a modification to the objective function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better than three other functions that have been proposed in the literature.

>>>>

As in face recognition, our system for metric learning is built by training a so-called triplet based `siamese triplet' network to learn to produce a small distance estimate for two surface forms for the same entity (between an arbitrarily chosen anchor and positive), and a large distance estimate for surface forms of different entities (an anchor and a negative).  A key problem in effective training of such networks is the problem of how to select negative pairs for training, because one cannot exhaustively show all negative pairs to the network.  In prior work for instance, this problem is solved by so-called `triplet mining' where so-called `semi-hard' negatives are gleaned after an all-pairs comparison of input vectors in a batch, e.g., \cite{DBLP:conf/cvpr/SchroffKP15}.  `Semi-hard' negatives are negatives that are further away from the anchor than positives, but not by a sufficient margin.  The idea of focusing on semi-hard negatives is to avoid mining noisy regions of the embedding space.  For matching across entity names, most positive forms for the entity names are actually substantially further away from the anchor than are negatives, as we show empirically in this paper.  In other words, `hard negatives' dominate the space, and are the norm.  Our approach to the problem of triplet mining for this problem was to use an approximate nearest neighbors algorithm to choose negatives for training that were in the nearest neighbor set, which means that most of the time, our negatives are `hard negatives', where the negative is closer to the anchor than positives.  This approach has three key benefits.  First, it lays out the entities based on their input vectors, and thus allows an efficient gathering of all nearest neighbors without a quadratic comparison of vectors in a batch to determine suitable negatives.  Second, it provides a baseline against which one can objectively measure the effects of training.  Third, it examines whether focusing on hard negatives is really detrimental to deep metric learning, at least for learning to map entity names in vector space.

We also investigated the effect of manipulating multiple local loss functions which have been proposed in the literature for improving deep metric learning, e.g., the triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, improved loss \cite{Zhang:2016:DML:3088616.3088665}, and angular loss \cite{DBLP:journals/corr/abs-1708-01682} functions.  For the problem of building models for people's names, we found that an adaptation to the objective function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better than three other functions that have been proposed in the literature.

### 2018-09-02 paper2018/relatedWork.tex
removing some equations

The idea of building joint embeddings for merging followed by nearest neighbors search has been applied recently to the problem of linking relational tuple embeddings with embeddings of other relational tuples or unstructured text \cite{Bordawekar18}, \cite{IDEL18}).  For the problem of linking tuples, each model that is learnt is specific to the database it was trained on.  Our contribution is that we developed general purpose embedding models for merging alternate surface forms of key entities such as people and companies leveraged from linked open data.  Once such models are built, they can be applied to joining any two datasets that share that semantic type.

Metric learning is a well studied problem in the face recognition literature, e.g., \cite{DBLP:conf/cvpr/2014}, \cite{DBLP:conf/cvpr/SchroffKP15}, with a rich literature in triplet mining techniques.  The closest approach to ours is the use of nearest neighbors algorithms for triplet mining has been applied by \cite{DBLP:journals/corr/KumarHC0D17}, but their focus is on a common practice in the literature which is focusing on mining semi-hard negatives, that is focusing on negatives where at least one positive is closer to the anchor.  In general, this means that one cannot look at fixed neighborhood sizes in building triplets.  In other words, if all the positives are further away from the anchor than the negatives in a given neighborhood size of $k$, it means that $k$ needs to be expanded until a neighborhood size is found that has the right characteristics (i.e., at least one positive that is closer than the negatives which can be chosen).  Our approach much more efficient because it relies on a fixed $k$ to generate samples, and shows that at least in the names domain, learning with hard negatives is effective.

The study of loss function effectiveness in metric learning is also a rich literature, with two basic types of loss functions that have been proposed: (a) local loss functions such as triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, angular loss \cite{Zhang:2016:DML:3088616.3088665} and improved loss \cite{DBLP:journals/corr/abs-1708-01682}, and (b) loss functions that operate on a more global level across a batch of training examples \cite{NIPS2016_6200}, \cite{songCVPR17}.  Our focus in this paper is on local loss functions.

>>>>

The idea of building joint embeddings for merging datasets followed by nearest neighbors search has been applied recently to the problem of linking relational tuple embeddings with embeddings of other relational tuples or unstructured text \cite{Bordawekar18}, \cite{IDEL18}).  For the problem of linking tuples, each model that is learnt is specific to the database it was trained on.  Our contribution is that we developed general purpose embedding models for merging alternate surface forms of key entities such as people and companies leveraged from linked open data.  Once such models are built, they can be applied to joining any two datasets that share that semantic type.

Metric learning is a well studied problem in the face recognition literature, e.g., \cite{DBLP:conf/cvpr/2014}, \cite{DBLP:conf/cvpr/SchroffKP15}, with a rich literature in triplet mining techniques.  The closest approach to ours is the use of nearest neighbors algorithms for triplet mining has been applied by \cite{DBLP:journals/corr/KumarHC0D17}, but their focus is on a common practice in the literature which is focusing on mining semi-hard negatives.  This means that one cannot look at fixed neighborhood sizes in building triplets.  If all the positives are further away from the anchor than the negatives in a given neighborhood size of $k$, it means that $k$ needs to be expanded until a neighborhood size is found that has the right characteristics (i.e., at least one positive that is closer than the negatives which can be chosen).  Our focus on `hard negatives' means we can use a fixed $k$ to generate samples.  At least in the names domain, metric learning with hard negatives is effective.

The study of loss function effectiveness in metric learning is also a rich literature, with two basic types of loss functions that have been proposed: (a) local loss functions such as triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, angular loss \cite{Zhang:2016:DML:3088616.3088665} and improved loss \cite{DBLP:journals/corr/abs-1708-01682}, and (b) loss functions that operate on a more global level across a batch of training examples \cite{NIPS2016_6200}, \cite{songCVPR17}.  Our focus in this paper is on local loss functions because many of the global loss functions seem to try and accomplish the same objective as hard triplet mining \cite{songCVPR17} using an indirect mechanism to do so.  Our approach directly mines hard triplets, so there is no need to try to broaden the loss function to a batch.

### 2018-09-02 paper2018/siamese_networks.tex
type o
removing some equations

These three input vectors from each triplet are fed to three identical networks that share the same weights.  Weight sharing ensures that the networks learn the same mapping function for any given input vector.  In our implementation, each of the three networks had 4 stacked layers of 128 unit Gated Recurrent Units (or GRUs) to capture the sequential nature of the input.  For name and textual data, positional information is critical, so we used GRUs instead of the convolutional neural networks (CNNs) that have been traditionally used in metric learning for face and image recognition.

GRUs are a type of recurrent network \cite{cho-al-emnlp14} where each hidden unit updates its weights at a specific step in the sequence $t$ based on the current input $x_t$ and the value of the hidden unit from the prior step $h_{t-1}$.  $r_t$ is a reset gate which determines whether the state from the previous step $h_{t-1}$ should be ignored. $z_t$ is an update gate which determines whether the current hidden state should be updated with the new hidden state $\tilde{h_t}$.  Equations~\ref{eq_1}-\ref{eq_4} that govern the update at $h_t$, as summarized by \cite{colah}.
\begin{equation}
z_t = \sigma(W_z . [h_{t-1}, x_t])
\label{eq_1}
\end{equation}

\begin{equation}
r_t = \sigma(W_r . [h_{t-1}, x_t])
\label{eq_2}
\end{equation}

\begin{equation}
\tilde{h_t} = tanh (W . [r_t * h_{t-1}, x_t])
\label{eq_3}
\end{equation}

\begin{equation}
h_t = (1- z_t) * h_{t-1} + z_t * \tilde{h_t}
\label{eq_4}
\end{equation}

The output of the last layer shown in the Figure~\ref{siamese_nets} as a dark gray layer produces an output vector embedding for the inputs.  These are fed to two layers which compute a euclidean distance between the \textit{anchor} and the \textit{positive} elements of a triplet (\textit{positive distance}), and the \textit{anchor} and the \textit{negative} elements of a triplet (\textit{negative distance}).  Conceptually, there are two objectives in metric learning, one to minimize \textit{positive distances}, and the other to maximize \textit{negative distances}.  As described below, this dual objective can be achieved by different loss functions.  We restrict ourselves to a discussion of the some of the more popular loss functions that are local in nature (i.e., they only look at a single triple).

@@

\begin{equation}
  l_{triple} =  \|\bf{x_a} - \bf{x_p}\|^2 + \left[ \alpha - \|\bf{x_a} -\bf{x_n} \right]_+^2
\label{adapted}
\end{equation}

>>>>

These three input vectors from each triplet are fed to three identical networks that share the same weights.  Weight sharing ensures that the networks learn the same mapping function for any given input vector.  In our implementation, each of the three networks had 4 stacked layers of 128 unit Gated Recurrent Units (or GRUs) to capture the sequential nature of the input.  For name and textual data, positional information is critical, so we used GRUs instead of the convolutional neural networks (CNNs) that have been traditionally used in metric learning for face and image recognition. GRUs are a type of recurrent network \cite{cho-al-emnlp14} where each hidden unit updates its weights at a specific step in the sequence $t$ based on the current input $x_t$ and the value of the hidden unit from the prior step $h_{t-1}$.

%$r_t$ is a reset gate which determines whether the state from the previous step $h_{t-1}$ should be ignored. $z_t$ is an update gate which determines whether the current hidden state should be updated with the new hidden state $\tilde{h_t}$.  Equations~\ref{eq_1}-\ref{eq_4} that govern the update at $h_t$, as summarized by \cite{colah}.
%\begin{equation}
%z_t = \sigma(W_z . [h_{t-1}, x_t])
%@\label{eq_1}
%\end{equation}

%\begin{equation}
%r_t = \sigma(W_r . [h_{t-1}, x_t])
%\label{eq_2}
%\end{equation}

%\begin{equation}
%\tilde{h_t} = tanh (W . [r_t * h_{t-1}, x_t])
%\label{eq_3}
%\end{equation}

%\begin{equation}
%h_t = (1- z_t) * h_{t-1} + z_t * \tilde{h_t}
%\label{eq_4}
%\end{equation}

The output of the last layer shown in the Figure~\ref{siamese_nets} as a dark layer produces an output vector embedding for the inputs.  These are fed to two layers which compute a euclidean distance between the \textit{anchor} and the \textit{positive} elements of a triplet (\textit{positive distance}), and the \textit{anchor} and the \textit{negative} elements of a triplet (\textit{negative distance}).  Conceptually, there are two objectives in metric learning, one to minimize \textit{positive distances}, and the other to maximize \textit{negative distances}.  As described below, this dual objective can be achieved by different loss functions.  We restrict ourselves to a discussion of the some of the more popular loss functions that are local in nature (i.e., they only look at a single triple).

@@

\begin{equation}
  l_{triple} =  \|\bf{x_a} - \bf{x_p}\|^2 + \left[ \alpha - \|\bf{x_a} -\bf{x_n}\| \right]_+^2
\label{adapted}
\end{equation}

### 2018-09-02 paper2018/triplet_selection.tex
removing some equations

\section{Triplet Selection}
Deep metric learning for faces is a difficult problem for neural networks to learn because improper sample selection can make it difficult for the network to converge.  We describe a popular approach from the face recognition literature first before we describe a new mechanism for triplet selection.

@@

Figure~\ref{triplet_selection} shows the triplet selection mechanism used in their work.  In practice, instead of focusing on finding \textit{hard positives}, they instead pair every possible positive in the sample shown in the right panel in the figure with selected negatives, since the set of positives is usually quite small.  Furthermore, for negative examples, they try to select what they term \textit{semi-hard negatives} instead of \textit{hard negatives}, where a \textit{semi-hard negative} has the property that $\|x_a - x_p \|^2 < \|x_a - x_n \|^2$.  As shown in the figure~\ref{triplet_selection} a \textit{semi-hard negative} is further from the \textit{anchor} than the \textit{positive}, but is not distant enough.  That is, the loss function still needs to move it closer to the margin $\alpha$ that is used in the triplet-loss function.  Schroff et al. further argue selecting \textit{hard negatives} such as $C$ in the figure may in fact lead to bad local minima early on in training, and lead to a collapsed model where the function always learns to return a value of 0, regardless of the pair being considered.

@@

Assuming one has the entire dataset indexed in an ANN index, the problem of triplet selection can be simplified by asking the ANN index for the top k-nearest neighbors of an \textit{anchor}, where k is given by the number of triplets that one desires to generate for each anchor.  As in earlier work, selection of \textit{hard positives} is not really relevant because all positive data should be used to teach the network the right function.  Selection of negatives is the set of all nearest neighbors that are \textit{negatives}.  There is no explicit attempt to filter out\textit{hard negatives} in the approach.  The overall idea is that the set of negatives that appear in the nearest neighbor set at input are in fact the most important elements for the network to learn to discriminate from positives.  Focusing on these elements, regardless of whether they are \textit{hard} or \textit{semi-hard} should lead to better learning.

An ANN-based strategy works better than the batch based triplet selection approach on two counts.  First, the entire dataset is in fact used in the triplet selection process.  Second, it yields an important baseline to assess what if any learning was performed by the neural network in mapping input vectors to a different space.

>>>>

\section{Triplet Selection}
As discussed earlier, deep metric learning for faces is a difficult problem for neural networks to learn because improper sample selection can make it difficult for the network to converge.  We describe a popular approach batch based approach from the face recognition literature first to contrast it with our mechanism for triplet selection.

@@

Figure~\ref{triplet_selection} shows the triplet selection mechanism used in their work.  In practice, instead of focusing on finding \textit{hard positives}, they instead pair every possible positive in the sample shown in the right panel in the figure with selected negatives, since the set of positives is usually quite small.  Furthermore, for negative examples, they try to select \textit{semi-hard negatives} instead of \textit{hard negatives}, where a \textit{semi-hard negative} has the property that $\|x_a - x_p \|^2 < \|x_a - x_n \|^2$.  As shown in the figure~\ref{triplet_selection} a \textit{semi-hard negative} is further from the \textit{anchor} than the \textit{positive}, but is not distant enough.  That is, the loss function still needs to move it closer to the margin $\alpha$ that is used in the triplet-loss function.  Schroff et al. further argue selecting \textit{hard negatives} such as $C$ in the figure may in fact lead to bad local minima early on in training, and lead to a collapsed model where the function always learns to return a value of 0, regardless of the pair being considered.

@@

Assuming one has the entire dataset indexed in an ANN index, the problem of triplet selection can be simplified by asking the ANN index for the top k-nearest neighbors of an \textit{anchor}, where k is given by the number of triplets that one desires to generate for each anchor.  As in earlier work, selection of \textit{hard positives} is not really relevant because all positive data should be used to teach the network the right function.  Selection of negatives is the set of all nearest neighbors that are \textit{negatives}.  There is no explicit attempt to filter out\textit{hard negatives} in the approach.  The overall idea is that the set of negatives that appear in the nearest neighbor set at input are in fact the most important elements for the network to learn to discriminate from positives for a join.  Focusing on these elements, regardless of whether they are \textit{hard} or \textit{semi-hard} should lead to better discrimination for joins.  An ANN-based strategy also provides an important baseline to assess what if any learning was performed by the neural network in mapping input vectors to a different space.
